Title

### 2024-06-10 paper/main.tex
Updates

In the case when $ \bm{Z} \neq \emptyset $, then partial correlations can be
used. This requires using two linear regression models: $ E_X: X \sim \bm{Z} $
and $ E_Y: Y \sim \bim{Z} $. Then computing the residuals using these two
regressions as: $ R_X = X - E_X(\bm{Z}) $ and $ R_Y = Y - E_Y(\bm{Y}) $. After
this a simple correlation coefficient can be computed between $ R_X $ and $ R_Y $.

@@

To compare how well this manual appraoch assisted by the suggested modications
perform compared to automated learning algorithms, we performed an analysis
using simulated data and simulating an expert. To construct the model using
suggestions, we start with a model with no edges, and take a greedy approach
for adding edges. At any point, we select to add an edge between variables that
have the highest conditional association between them. A simulated expert is
then asked to specify the direction for the edge. Given an accuracy of the
expert $ \alpha $, the expert either gives the correct direction, incorrect
direction, or can specify do not know as:

@@

If the expert says `do not know` for any of the edges, the edge is not prompted
again to the expert. We also make sure that only edges which do not form a
cyclic in the graph are used to select the next potential edge. After adding
each edge, we also check if the p-value of any existing edge shows
independence. If that happens we remove that edge and blacklist that edge,
i.e., that edge is not prompted again during the run of the algorithm. We
repeat this procedure till the model explains all correlations between the
variables. There is a possibility that this greedy expert gets stuck at
incorrect graph structures as it does not do any backtracking to fix its
earlier mistakes. This procedure is outlined in the Algorithm.
\todo[inline]{Add the algorithm}

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/shd_ribbon.pdf}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\includegraphics{../code/plots/sid_ribbon.pdf}
	\end{subfigure}
\end{figure}

>>>>

In the case when $ \bm{Z} \neq \emptyset $, then partial correlations can be
used. This requires using two linear regression models: $ E_X: X \sim \bm{Z} $
and $ E_Y: Y \sim \bm{Z} $. Then computing the residuals using these two
regressions as: $ R_X = X - E_X(\bm{Z}) $ and $ R_Y = Y - E_Y(\bm{Y}) $. After
this a simple correlation coefficient can be computed between $ R_X $ and $ R_Y $.

@@

We analyzed the performance of this manual approach by comparing it with two
automated algorithms: PC and Hill-Climb Search. For the comparison we use
simulated data from a known DAG and compare how well the algorithm is able to
recover the original model using two metrics: Structural Hamming Distance (SHD)
and Structural Intervention Distance (SID). To simulate the data, we start with
a randomly generated DAG and use linear models with random effects to generate
the data. We repeat the data generation $ 30 $ times for each density value for
the DAG. As both PC and Hill-Climb Search can only give us a CPDAG, we compare
the orientation of these CPDAG which result in the best and worst case scores
on SHD and SID. This procedure is outlined in Algorithm 1.

\todo[inline]{Add the algorithm}

To simulate an expert using this assisted model construction approach, we start
with an empty model and take a greedy approach to add edges to this model. At
any point, we select the pair of variables that has significant correlation and
the highest unexplained correlation, i.e., highest conditional association. We
then use an oracle to decide the direction of the edge between the variables.
Given an accuracy of the oracle, $ \alpha $, the oracle either gives the
correct direction, incorrect direction, or returns None representing that it
does not know the direction.

@@

If the oracle returns None for any pair of variables, an edge between this pair
is not suggested to the oracle in future iterations. We also make sure that
only edges which do not form a cyclic in the graph are used to select the next
potential edge. After adding each edge, we also check if the p-value of any
existing edge shows independence. If that happens we remove that edge and
blacklist that edge, i.e., that edge is not prompted again during the run of
the algorithm. We repeat this procedure till the model explains all
correlations between the variables. There is a possibility that this greedy
expert gets stuck at incorrect graph structures as it does not do any
backtracking to fix its earlier mistakes. This procedure is outlined in the
Algorithm.
\todo[inline]{Add the algorithm}

\subsection{Results}
\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/shd_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/sid_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\caption{Comparison of PC and Hill-Climb Search algorithms against }
\end{figure}
